% 02-abbreviations.tex - Section 2: Abbreviations

\chapter{Abbreviations and Definitions}
\label{sec:abbreviations}

\section{Abbreviations}

\begin{longtable}{p{3cm}p{10cm}}
    \toprule
    \textbf{Abbreviation} & \textbf{Definition} \\
    \midrule
    \endfirsthead

    \toprule
    \textbf{Abbreviation} & \textbf{Definition} \\
    \midrule
    \endhead

    \bottomrule
    \endfoot

    ARX & Analog Receiver \\
    ASP & Analog Signal Processor \\
    AT1 & First Attenuator (0--30~dB in 2~dB steps) \\
    AT2 & Second Attenuator (0--30~dB in 2~dB steps) \\
    AT3 & Third Attenuator (0--15.5~dB in 0.5~dB steps) \\
    dB & Decibel \\
    FEE & Front End Electronics \\
    FIL & Filter selection command \\
    FPW & FEE Power command \\
    HPF & High-Pass Filter \\
    I2C & Inter-Integrated Circuit (communication bus) \\
    ICD & Interface Control Document \\
    LED & Light Emitting Diode \\
    LOC & Locate LED command \\
    LPF & Low-Pass Filter \\
    LWA & Long Wavelength Array \\
    M\&C & Monitor and Control \\
    MCS & Monitor and Control System \\
    MIB & Management Information Base \\
    MJD & Modified Julian Date \\
    MPM & Milliseconds Past Midnight \\
    PSU & Power Supply Unit \\
    QMA & Quick Miniature A (RF connector type) \\
    RS-485 & Serial communication standard \\
    SAMD21 & Microchip SAM D21 ARM Cortex-M0+ microcontroller \\
    SPI & Serial Peripheral Interface \\
    UDP & User Datagram Protocol \\
    USB & Universal Serial Bus \\

\end{longtable}

\section{Definitions}

\begin{description}
    \item[Stand] A single antenna structure consisting of two polarizations (X and Y). Each stand is identified by a unique number from 1 to 256.

    \item[Board] An ARX board that services multiple stands. In the current configuration, each board handles 8 stands.

    \item[Chassis] An enclosure containing multiple ARX boards and associated power supplies.  In the current configuration, a chassis can hold up to 8 boards.

    \item[Filter Code] A numeric code (0--7) that selects the combination of high-pass and low-pass filters applied to the signal.

    \item[Attenuator Setting] A numeric value that determines the signal attenuation level for each attenuator stage.
\end{description}
